\Title

### 2016-02-09 manuscript/manuscript.tex
Caption for problem concept sketch

% Document metadata
% =================
\newcommand{\Title}{
    Fast non-linear gravity inversion in spherical coordinates:
    application to the South American Moho
}
\newcommand{\Keywords}{
        Moho;
        gravity inversion;
        spherical coordinates;
        tesseroid;
        South America
}
\title[]{\Title}
\author[]{
    Leonardo Uieda$^{1,2}$,
    Valéria C. F. Barbosa$^{2}$
    \\
    $^1$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.
    e-mail: leouieda@gmail.com
    \\
    $^2$Observatório Nacional, Rio de Janeiro, Brazil.
}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/problem-concept}
    \caption{Sketch explaining disturbance and parametrization from ON seminar.}
    \label{fig:anomalysketch}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda2015},
        available at
        \url{http://dx.doi.org/10.6084/m9.figshare.1495525}.
    }
    \label{fig:tesseroid}
\end{figure}

>>>>

% Document metadata
% =================
\newcommand{\Title}{
    Fast non-linear gravity inversion in spherical coordinates
    with application to the South American Moho
}
\newcommand{\Keywords}{
        Moho;
        gravity inversion;
        spherical coordinates;
        tesseroid;
        South America
}
\title[]{\Title}
\author[]{
    Leonardo Uieda$^{1,2}$,
    Valéria C. F. Barbosa$^{2}$
    \\
    $^1$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.
    e-mail: leouieda@gmail.com
    \\
    $^2$Observatório Nacional, Rio de Janeiro, Brazil.
}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/problem-concept}
    \caption{
        Sketch of the stages in gravity data correction and
        the discretization of the anomalous Moho relief using tesseroids.
        (a) The Earth and the measured gravity at point P ($g(P)$).
        (b) The Normal Earth and the calculated normal gravity at point P
        ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
        (c) The gravity disturbance ($\delta(P)$) and
        the corresponding density anomalies after removal of the normal gravity:
        topography, oceans, crustal heterogeneities, and the anomalous Moho.
        (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic
        correction and the remaining density anomalies.
        (e) All density anomalies save the anomalous Moho are assumed to have
        been removed before inversion.
        (f) The discretization of the anomalous Moho in tesseroids. Grey
        tesseroids will have a negative density contrast while red tesseroids
        will have a positive one.
    }
    \label{fig:anomalysketch}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda2015}.
    }
    \label{fig:tesseroid}
\end{figure}
